\section{Discussion and conclusion}\label{sec:discussion}

This paper asked who bears the 2025 US tariffs on UK goods after the tax--benefit system responds, and answered by deriving the shock from primitives---the tariff schedule, HMRC trade-by-SIC exposure, and an outturn-anchored export-demand elasticity---and passing it through PolicyEngine UK under four adjustment margins. Three conclusions stand.

First, the adjustment margin, not the tariff rate alone, determines what the shock \emph{is} when it reaches households---and the direction of that determination reverses the naive prior. The UK tax--benefit system cushions an in-work wage cut (41 per cent) more than an earnings-equivalent wave of job losses (33 per cent), and the decomposition of Section~\ref{sec:results-mechanism} shows why: income tax relieves a wage cut at marginal rates but a lost job only at average rates (35 versus 20 pence per pound of gross loss), and Universal Credit---though it responds more to displacement, as the naive intuition predicts---reaches only a third of displaced workers' families, gated in the model by take-up and the joint partner-income taper rather than by the capital limit, which the plain FRS data (carrying no household capital) cannot exercise. Statutory generosity toward the unemployed is not economic generosity once the gates bind on the population actually displaced. The fiscal ordering is the mirror image, though it is suggestive rather than sharply identified: the deterministic wage-cut margin costs the Exchequer \pounds 0.98 billion a year under the full schedule against a displacement mean of \pounds 0.85 billion $\pm$ 0.30 across 50 draws---an ordering that holds in 37 of 50 draws but whose \pounds 0.13 billion gap sits inside one draw-to-draw SD---while only the displacement margin moves poverty at all ($+0.055 \pm 0.021$ percentage points versus approximately zero).

Second, on the displacement margin the shock is regionally, not vertically, concentrated. Displaced manufacturing earnings sit in deciles 7--10, so national inequality and poverty statistics barely register a shock whose Monte Carlo mean regional losses reach \pounds 60--110 per person per year in the hardest-hit regions---and, within any single realisation, \pounds 100--200 per head in whichever handful of regions the displacement draw lands on. Trade-shock incidence in the UK is a geography problem wearing the clothes of a distribution problem---consistent with the China-shock literature's regional persistence findings \citep{autor2021, dixcarneirokovak2017} but established here at the household, rules-based level.

Third, the Economic Prosperity Deal was worth about $6{,}500$ jobs (the mean paired-draw difference over 50 displacement draws, $\pm 4{,}388$, positive in 47 of 50; the analytic quota expectation is $6{,}857$), \pounds 0.38 billion of gross earnings and roughly \pounds 0.2 billion a year to the Exchequer on the direct channel (a mean paired-draw difference of \pounds 0.19 billion $\pm$ 0.38, positive in 36 of 50 draws)---real but modest, concentrated in autos, with the pharmaceutical clause's true cost routed through the NHS rather than the labour market and the steel clause largely beside the sector's EU-dominated exposure.

\medskip
\noindent\textbf{Limitations.} Seven are worth stating plainly. (1) The inactivity margin now carries its own fiscal machinery---inactive over-50s receive the UC LCWRA health element---but two caveats remain. The assumption that every displaced worker aged 50 and over passes the Work Capability Assessment is deliberately an upper bound on the health-element route, and no assessment process, waiting period, or conditionality regime is modelled: the WCA is a gatekeeping institution whose pass rates respond to local labour-market slack \citep{robertstaylor2022}, and the health-related caseload was already at a post-pandemic high when the tariffs arrived \citep{ifs2024}, so realised flows could sit anywhere between the 50-per-cent sensitivity variant and the upper bound. (2) Monte Carlo dispersion is large relative to the means (\pounds 0.30 billion SD against \pounds 0.7--0.9 billion means over 50 draws), so only orderings that survive it are asserted; the displacement--wage-cut fiscal gap in particular (holding in 37 of 50 draws) is identified by the aggregate cushioning accounting rather than by the draws. (3) Absolute BHC poverty against a fixed baseline line is computed manually outside the model, which lacks an \texttt{in\_absolute\_poverty\_bhc} variable in this version. (4) The central analysis covers the direct exposed-sector earnings channel only. Upstream supply-chain propagation---which the production-network literature finds can multiply direct effects severalfold \citep{barrotsauvagnat2016, acemoglu2016}---is now bounded in Appendix~\ref{app:supplychain}: a Leontief round through the ONS domestic input-output tables roughly doubles the gross earnings loss (amplification factor 1.95), pulls wholesale, transport and professional services into the exposed set, and leaves every structural ordering intact. Still omitted are downstream and induced-consumption rounds, local-multiplier ripple effects, which US and German estimates put at 0.4--1.6 additional local jobs per lost tradable job \citep{moretti2010, gathmann2020}, general-equilibrium wage responses, the exchange-rate offset \citep{corsettilloydostry2025}, and retaliation; fiscal policy is held fixed throughout---\citet{ignatenko2025} show revenue recycling can flip aggregate employment signs, so the fiscal numbers are first-round incidence, not equilibrium outcomes. The 0.06-per-cent-of-GDP gross shock should be read as a lower bound on the all-channel effect, which the OBR puts at one-third to three-quarters of a per cent permanently (about 1 per cent at peak in its reciprocal scenario). The omitted channels are largely additive: the Leontief round (1.95) compounded with local multipliers (roughly 1.4--2.6) implies an all-channel figure of about 2.7--5.1 times the direct earnings shock, 0.16--0.31 per cent of GDP, which approaches the OBR range from below. (5) No behavioural margin is active on the household side. The reallocation family of Section~\ref{sec:results-reallocation} does now move workers explicitly between sectors---directly answering the objection that after the China shock displaced manufacturing workers went into healthcare, delivery and retail rather than staying unemployed \citep{autor2014, dauth2021}---so the earlier limitation that no family moved anyone between sectors no longer stands. What remains is narrower but real: who reallocates is \emph{assumed} (it is the displacement draw, with destinations assigned on FRS employee-weight shares) rather than estimated, no worker is allowed to reallocate partially or to fail to reallocate, and \texttt{sic\_industry\_division} has no downstream effect in the tax--benefit calculation, so the sector switch is literal but all the economic content sits in the earnings and hours penalty. Added-worker responses, retirement timing and self-employment entry \citep{irastorza2025} are still suppressed, as are labour-supply responses to the tax and benefit changes themselves. (6) The constituency layer is illustrative only and is confined to Appendix~\ref{app:constituency}: its industry codes are imputed on a different dataset and period, so it cannot reproduce observed local industry mix, and its seat ranking should not be read against exposure-based analyses that can \citep{cityredi2025, centreforcities2025}. (7) The trade numerator is on the HMRC RTS/OTS customs basis (\pounds 55.6 billion of 2024 US exports, \pounds 52.5 billion mapped to SIC divisions), which sits below the ONS balance-of-payments basis (about \pounds 59.3 billion); intensities inherit that coverage gap.

\medskip
\noindent\textbf{Further work.} Beyond modelling the WCA gate itself (assessment rates, waiting periods, conditionality), three directions. A \emph{measured-margin} family calibrated to the accumulating 2025--26 outturn (ONS trade, BICS, SMMT), replacing the stylised poles with the displacement/wage-cut mix the data actually chose, in the spirit of \citet{rud2022}'s decomposition. Sharpening the constituency geography of Section~\ref{sec:results-regions}---now mapped across all 650 Westminster seats, but on imputed industry codes and a single draw---with observed local industry structure (BRES employment by SIC) replacing the demographic imputation. And dynamic transition paths---re-employment hazards, scarring, and the multi-year fiscal tail that \citet{dixcarneiro2014} and \citet{beatty2017} both imply a one-year snapshot understates.

The bottom line inverts where the paper began. The 2025 tariff reaches UK households mainly as a public-finance event, not a poverty event; and the arm of the welfare state that absorbs it best is not the safety net for the jobless but the automatic machinery that relieves every pound of in-work earnings at the marginal tax rate, with no claim to make and no gate to pass.
