\section{Introduction}\label{sec:intro}

Who bears a foreign tariff shock after the tax--benefit system responds---and how much does the answer depend on whether workers adjust through job loss, wage cuts in place, exit into economic inactivity, or reallocation into lower-paid services work? In April 2025 the United States imposed a 10 per cent baseline tariff on UK goods, with 25 per cent rates on cars and steel; the May 2025 Economic Prosperity Deal (EPD) cut the auto rate to 10 per cent on a 100,000-vehicle quota, offered conditional steel relief, and---in a December 2025 side agreement paid for through NHS pricing concessions---exempted pharmaceuticals. A rich institutional literature has traced the macroeconomic, sectoral, regional and firm-level consequences of this shock \citep{obr2025, boe2025, cityredi2025, centreforcities2025}. None of it reaches the household: no analysis passes the tariff through to disposable income, poverty, or the benefit system that would actually cushion it. This paper fills that cell.

The design is primitives-first. The shock enters as the tariff schedule itself, combined with US-export intensity by SIC division (ONS/HMRC trade-by-SIC) and an export-demand elasticity, to yield sector-level earnings shocks; the elasticity (2.0) is anchored on the realised outturn---US-bound goods exports fell 24.7 per cent in the first full tariff month against a 12.8 per cent trade-weighted tariff---and cross-checked against UK worker-level trade-shock estimates \citep{delyonpessoa2021} and the OBR and \citet{ignatenko2025} aggregate anchors. Employment is an \emph{outcome} of the derived shock, not a free input. The derived sector shocks are then realised on Family Resources Survey workers in exposed industries under four adjustment-margin families: \emph{displacement} into unemployment (the China-shock short run of \citealp{autor2013}), \emph{wage cuts with reallocation} into other sectors (the German and Danish long run of \citealp{dauth2021} and \citealp{traiberman2019}), and \emph{exit into inactivity} for older displaced workers---the margin UK deindustrialisation actually chose, when coalfield and steel job losses became benefit-financed economic inactivity rather than measured unemployment \citep{beatty2007, beatty2017}, and \emph{reallocation into services}---the same displaced workers re-employed in retail, health, land transport and food service at an FRS-calibrated 28.3 per cent annual-earnings penalty, the margin the China-shock evidence actually describes \citep{autor2014, dauth2021}. The first three hold the aggregate earnings loss fixed; the fourth removes only the wage penalty on movers, and so is level-comparable with displacement (identical worker sets, paired draws) and rate-comparable with all. PolicyEngine UK, an open-source tax--benefit microsimulation model, computes disposable income, poverty, inequality and the Exchequer position under each.

The adjustment margin is the paper's central axis, and the result it delivers is about the \emph{reliability} of insurance rather than its generosity. The naive reading of Universal Credit says the system should replace a job loss more generously than it tops up an in-work wage cut of equal aggregate size. On the microdata the two are cushioned to a similar degree: at a defensible 80 per cent take-up among newly entitled families, the system absorbs $38.9 \pm 3.7$ per cent of an earnings-equivalent displacement shock against 41.0 per cent of a proportional wage cut (EPD schedule: $37.8 \pm 5.1$ against 40.8). The remaining two-to-three-point gap sits well inside the draw-to-draw standard deviation and we do not claim it is separately identified. \emph{What is sharp is the composition.} An exact, residual-free decomposition shows the two margins reaching similar totals through opposite instruments. Wage cuts are cushioned overwhelmingly by income tax---35.2 of the 41.0 points, relief at every worker's \emph{marginal} rate---with Universal Credit contributing 1.5. Job losses draw 19.7--21.2 points from income tax, because displacement destroys the whole earnings stream and so is relieved only at the \emph{average} rate, and 9.5--9.9 points from Universal Credit. Across a five-point grid of take-up rates the income-tax component of displacement cushioning \emph{never moves} (21.2 points at every rate under the full schedule) while the UC component swings from 6.2 to 12.1; and the wage-cut margin is \emph{exactly} invariant to take-up (spread 0.0, by construction: a pay cut creates no new claimants). Displacement cushioning therefore swings roughly seven points on claiming behaviour alone, while wage-cut cushioning cannot move at all. That is the paper's headline: the UK system protects both margins to a similar extent, but wage-cut protection is automatic and mechanical---it happens through the tax schedule whether or not anyone acts---while job-loss protection is contingent on clearing eligibility gates and actually claiming. In the language of \citet{atkin2025}, statutory generosity toward the unemployed is not economic generosity until the gates are cleared. An earlier treatment of this paper reported a much larger, 8-point level gap in favour of the wage-cut margin; that figure is retracted in Section~\ref{sec:results-cushioning}, where its source---a stale baseline claiming flag carried forward through the shock---is documented. The marginal-versus-average asymmetry itself is not new---\citet{auerbachfeenberg2000} originate the reading of the income tax as a marginal-rate stabiliser, \citet{mckayreis2016} formalise the role of progressivity and of the intensive/extensive structure of shocks, and \citet{dolls2012} find the tax term larger for the intensive shock in all nineteen EU countries and the United States. Three things here are: the \emph{contingency result} itself, which is a statement about the variance of stabilisation with respect to claiming behaviour rather than about its level, and which is robust to the take-up assumption in a way a level gap is not; an exact, residual-free decomposition computed on the population \emph{actually displaced} rather than on a proportional shock applied to everyone; and a gate-by-gate audit that counts which UC constraint binds on each displaced family. The corrected treatment also \emph{validates} against the closest benchmark rather than departing from it: our 38.9 per cent sits close to \citet{dolls2012}'s UK unemployment-shock cell of 0.415, with the modest residual attributable to a displaced population of above-median manufacturing earners with partners in work, on whom the joint partner-income taper bites. Two scope limits travel with the design: the wage-cut family models the earnings consequence of reallocation without moving anyone between sectors, and household behavioural margins---added-worker responses, retirement timing, self-employment entry \citep{irastorza2025}---are suppressed throughout. Whichever margin, the calibrated shock (a \pounds 1.8 billion annual gross earnings loss, 0.06 per cent of GDP on the direct channel) reaches households mainly as a fiscal event---\pounds 0.7--1.0 billion a year to the Exchequer (Monte Carlo means over 50 displacement draws)---rather than a poverty event (at most $+0.05$ percentage points); and on the displacement margin it is regionally, not vertically, concentrated, with losses landing in deciles 7--10 of the income distribution while averaging \pounds 55--105 per person per year in the hardest-hit regions---and reaching \pounds 100--200 per head in the few regions any single realisation lands on. Which margin the data chose is testable against the 2025--26 outturn (ONS trade, BICS, SMMT monthly series), and the historical UK evidence decomposing displacement costs into wage cuts versus non-employment spells \citep{rud2022} calibrates the split.

Two sectoral nuances discipline the headline claims. Steel carries a caveat: roughly 80 per cent of UK steel exports go to the EU, so the steel--Wales cell is more exposed to EU/UK safeguards than to US tariffs. And pharmaceuticals---exempted under the December 2025 deal in exchange for VPAG rebate cuts and NHS pricing concessions---is a fiscal and pricing channel, not an employment channel, and is treated as such. Finally, an EPD counterfactual (full tariffs versus deal-mitigated rates) prices what the deal was worth, sector by sector and region by region, to households and the Treasury. Following \citet{ignatenko2025}, revenue recycling can flip aggregate employment signs; we compute first-round fiscal incidence holding fiscal policy fixed.

The remainder of the paper proceeds as follows. Section~\ref{sec:literature} situates the study between the quantitative trade-incidence literature and tax--benefit microsimulation. Section~\ref{sec:methodology} sets out the tariff schedule, the trade-by-SIC exposure mapping, the derived sector shocks and the four adjustment-margin families. Section~\ref{sec:results} presents the results: the derived shocks and their outturn anchor, the cushioning result and its take-up contingency, the distributional, fiscal and regional incidence by margin, and the EPD counterfactual. Section~\ref{sec:policy} turns to the EPD counterfactual and policy responses. Section~\ref{sec:discussion} concludes.
