\section{Methodology}\label{sec:methodology}

\subsection{Design: primitives first}\label{sec:method-primitives}

The shock enters through primitives, not through an assumed employment effect. The pipeline is:
\begin{equation}
s_j \;=\; \tau_j \, x_j \, \varepsilon \, \pi,
\label{eq:shock}
\end{equation}
where $s_j$ is the derived earnings-shock size for SIC 2007 division $j$ (the fraction of the division's employee wage bill removed by the tariff), $\tau_j$ is the tariff rate faced by the division under the schedule, $x_j$ is its US-export intensity, $\varepsilon$ is the export-demand elasticity, and $\pi$ is the pass-through of the sector output loss to the sector wage bill. $x_j$ is US goods exports of the division as a share of division turnover, built from the HMRC uktradeinfo RTS/OTS API (2024 US exports, \pounds 52.5 billion mapped to SIC divisions of a \pounds 55.6 billion customs-basis total, via a documented SITC-to-SIC crosswalk) and ONS Annual Business Survey turnover denominators; Appendix~\ref{app:data} gives the full provenance and validation. The elasticity $\varepsilon = 2.0$ is anchored on the realised outturn: ONS data show UK goods exports to the US falling 24.7 per cent in April 2025, the first full tariff month, against a 12.8 per cent trade-weighted average tariff implied by the schedule and the built intensities ($0.247/0.128 = 1.93$, rounded to 2.0, mid-range of short-run trade elasticities). The pass-through $\pi = 1.0$ places the full sector output loss on the sector wage bill---the appropriate short-run displacement assumption. Because $\varepsilon$ and $\pi$ enter Equation~\eqref{eq:shock} only through their product, all pound-denominated results scale approximately linearly in $\varepsilon\pi$, while cushioning \emph{rates} and margin orderings are essentially invariant to it; Appendix~\ref{app:grid} verifies both properties on a $4 \times 3$ sensitivity grid over $\varepsilon \in \{1.0, 1.5, 2.0, 3.0\}$ and $\pi \in \{0.5, 0.75, 1.0\}$. Since the central $\varepsilon = 2.0$ is anchored on a single month's realised outturn (April 2025), the grid doubles as the uncertainty band around that anchor. The implied aggregate gross earnings loss under the full schedule is \pounds 1.77 billion a year, about 0.06 per cent of GDP on the direct exposed-sector channel, sensibly below the OBR's all-channel scenario range of 0.3--0.6 per cent \citep{obr2025} and consistent with the UK cell of \citet{ignatenko2025} and UK worker-level responses \citep{delyonpessoa2021, rud2022}. Employment is then an \emph{outcome} of $s_j$ under an assumed adjustment margin---never a free input. The design covers the direct exposed-sector channel only: local-multiplier estimates of 0.4--1.6 additional local jobs per lost tradable job \citep{moretti2010, gathmann2020} imply the all-channel employment effect is larger, so the derived shock is a lower bound (Section~\ref{sec:discussion}). Appendix~\ref{app:supplychain} bounds the first omitted channel directly, propagating the export-demand falls upstream through the ONS domestic input-output tables via a Leontief round \citep{barrotsauvagnat2016, acemoglu2016}.

\subsection{The tariff schedule and the EPD counterfactual}\label{sec:method-schedule}

Two tariff scenarios bracket the policy. \emph{Full tariffs}: the April 2025 schedule---10 per cent baseline on UK goods, 25 per cent on motor vehicles (SIC 29) and steel (SIC 24). \emph{EPD}: the deal-mitigated schedule---autos at the 10 per cent in-quota rate (100,000 vehicles, roughly the 2024 US export volume, so the quota binds only marginally); steel with conditional, partial relief; pharmaceuticals (SIC 21) exempt under the December 2025 agreement. The difference between the two scenarios, run through identical downstream machinery, prices the EPD for households and the Exchequer. Two caveats travel with the schedule. Steel: about 80 per cent of UK steel exports go to the EU, so the US tariff is a minority driver of the sector's exposure and the steel cell should be read alongside EU/UK safeguards. Pharmaceuticals: the exemption was purchased through VPAG rebate cuts and NHS pricing concessions, so pharma's incidence is fiscal and price-side, not an employment shock; we model its employment shock as zero under the EPD and discuss the fiscal channel separately (Section~\ref{sec:policy}).

\subsection{Adjustment-margin families}\label{sec:method-margins}

The derived $s_j$ is realised on Family Resources Survey 2024--25 employees in exposed divisions under three families, each holding the aggregate earnings loss $\sum_j s_j B_j$ (with $B_j$ the division wage bill) fixed:

\paragraph{Displacement (ADH short run).} Within each exposed division a weighted head-count quota $s_j \times$ (division employee weight) is drawn with uniform ordering keys, so a represented worker's displacement probability does not depend on their record's grossing weight; displaced workers move to unemployment with earnings, hours, pension contributions and statutory pay zeroed.
\paragraph{Wage cuts with reallocation (Dauth/Traiberman long run).} No job loss; every employee in division $j$ takes a proportional cut of $s_j$, so the weighted aggregate earnings removed equals $\sum_j s_j B_j$ by construction---exact earnings-equivalence with the displacement family's expected removal.
\paragraph{Inactivity (Beatty--Fothergill UK history).} The displacement draw, but displaced workers aged 50 and over exit to economic inactivity, the benefit-financed route of UK deindustrialisation, rather than unemployment. The route is benefit-financed in the model, not just relabelled: every inactive worker is flagged as having limited capability for work-related activity, so their household's Universal Credit includes the LCWRA health element (\pounds 217.26 a month in 2026; in policyengine-uk 2.89.2 the stored survey-imputed \texttt{uc\_LCWRA\_element} is overridden with the baseline element plus one annual LCWRA amount per newly flagged person, leaving all other households' stored elements untouched, and the run hard-errors if the element fails to reach any flagged person's benefit unit). This mirrors the \citet{beatty2007} route by which industrial job loss became incapacity-benefit inactivity. The strong assumption should be stated plainly: \emph{all} displaced workers aged 50 and over are assumed to pass the Work Capability Assessment, so the family is an upper bound on the health-element route; a sensitivity variant in which only 50 per cent of the older displaced qualify is reported alongside (Section~\ref{sec:results-margins}). Work-search conditionality carries no separate fiscal machinery in the model, so the LCWRA element is the entire modelled wedge between inactivity and unemployment.

The margin is the paper's central axis because the tax--benefit system treats the two poles asymmetrically: an in-work earnings reduction is offset automatically at marginal tax and taper rates, while a job loss moves the worker to the gated, means-tested extensive margin of the benefit system. Which pole the system cushions more is an empirical question the microdata answer---in the direction opposite to the naive replacement-rate intuition (Section~\ref{sec:results-cushioning}).

\subsection{Microsimulation and outcomes}\label{sec:method-microsim}

The realisation step---an externally derived shock imposed as status and earnings transitions on survey households, then run through the full benefit rules---follows \citet{brewertasseva2021}, who apply it to the Covid-19 labour-market shock in UKMOD, and the EUROMOD nowcasting tradition of imposed labour-market transitions \citep{navicke2013}. PolicyEngine UK computes baseline and shocked household disposable income (HBAI cash concept throughout), relative before-housing-costs poverty, absolute before-housing-costs poverty against a fixed baseline line (computed manually, since the installed model version exposes no absolute-poverty variable; Appendix~\ref{app:mc}), after-housing-costs poverty, the Gini coefficient of equivalised disposable income, decile and region breakdowns, and the Exchequer effect (foregone tax plus additional benefit spending, via the government balance). Displacement draws are Monte Carlo: every displacement/inactivity result is reported as the mean and standard deviation over $n$ draws (default 20). Following \citet{ignatenko2025}, revenue recycling can flip aggregate employment responses; we compute first-round incidence holding fiscal policy fixed and treat recycling as a policy counterfactual.
