\section{Policy}\label{sec:policy}

\subsection{What the Economic Prosperity Deal was worth}\label{sec:policy-epd}

Priced as the difference between the two tariff scenarios run through identical machinery (Section~\ref{sec:results-epd}), the EPD is worth, per year on the displacement margin: about $6{,}500$ manufacturing jobs (the mean paired-draw difference over 50 displacement draws, $\pm 4{,}344$, positive in 47 of 50; the analytic quota expectation is $6{,}857$), \pounds 0.38 billion of gross earnings, and roughly \pounds 0.2 billion to the Exchequer (\pounds 0.21 billion $\pm$ 0.39 mean paired-draw difference on the displacement margin, positive in 37 of 50 draws; \pounds 0.22 billion, deterministic, on the wage-cut margin). Relative BHC poverty impacts fall from $+0.047 \pm 0.016$ to $+0.038 \pm 0.020$ percentage points under displacement. These are modest absolute numbers---the direct earnings channel of the full schedule was itself only 0.06 per cent of GDP---but they are not evenly spread. The deal's value is a bundle of three sectoral clauses with three distinct geographies. The auto quota (100{,}000 vehicles at 10 per cent, approximately the 2024 US export volume, so the in-quota rate is the effective one) removes the single largest derived shock and is worth the most to the West Midlands and the wider vehicle supply chain. The pharmaceutical exemption removes the SIC 21 employment shock entirely, protecting a high-wage, geographically dispersed sector---but its price was paid through a different fiscal door (below). Steel relief, modelled at half the 25 per cent rate, is the weakest clause: it was conditional and slow to implement, it leaves Yorkshire and the Humber still exposed under EPD displacement (a Monte Carlo mean loss of \pounds 33 $\pm$ 35 per person per year; its worst single draw reaches \pounds 159, and \pounds 218 under the full schedule), and in any case the steel sector's binding trade-policy exposure is EU/UK safeguards, not the US tariff. What the deal did \emph{not} do is also visible in Table~\ref{tab:shocks}: machinery, electronics, aerospace and chemicals---which together account for more derived earnings loss than autos---remain at the 10 per cent baseline, which is why the EPD removes only about a fifth of the gross earnings shock.

\subsection{The pharmaceutical channel}\label{sec:policy-pharma}

The pharmaceutical exemption deserves its own accounting because its incidence is fiscal and price-side, not an employment shock---the cleanest illustration in this paper of statutory versus economic incidence \citep{atkin2025}. Statutorily, the December 2025 side agreement zero-rates UK pharmaceutical exports to the US for three years. Economically, the exemption was purchased through the NHS: the VPAG rebate rate on branded medicine sales was cut from 22.5 to 14.5 per cent, alongside NHS pricing concessions \citep{abpi2025}. With UK branded-medicine sales subject to VPAG in the tens of billions, an eight-percentage-point rebate cut is a large number by the standards of this paper's Exchequer figures. This is explicitly a back-of-envelope order-of-magnitude remark rather than a costing: the arithmetic is (VPAG-eligible branded sales base) $\times$ 0.08, and this paper neither builds that sales base nor models the NHS pricing concessions that travel with it, so no figure is asserted. The qualitative point stands and is the one that matters---the exemption was purchased, not granted, and the price sits on the health budget rather than in household earnings. This paper's employment-channel machinery correctly assigns pharma a zero shock under the EPD, but the reader should not conclude the exemption was free: its cost simply does not pass through household earnings, and therefore does not appear in a tax--benefit microsimulation. A full welfare accounting of the EPD would set the \pounds 0.2 billion annual Exchequer saving found here against the VPAG concession on the other side of the public balance sheet.

\subsection{Cushioning reforms}\label{sec:policy-reforms}

The cushioning result of Section~\ref{sec:results-cushioning} reframes the standard policy menu, though in a different direction from the one an earlier draft proposed. The two margins are cushioned to a similar degree; what differs is that job-loss protection is contingent on gates and claims while wage-cut protection is automatic. The decomposition of Section~\ref{sec:results-mechanism} locates the contingency: on these data the joint partner-income taper and modelled non-claiming between them leave about half of displaced workers' families with no UC at all, and the whole take-up grid moves the displacement cushioning rate by some seven points without moving its income-tax component at all. The policy target is therefore \emph{reliability}, not generosity---raising UC rates does nothing for a family that never enters an award calculation, and neither does it reduce the variance of what the displaced actually receive. Three directions follow, all simulable in this framework. First, gate easements for the involuntarily displaced: automatic enrolment (or an assumed-take-up presumption) after redundancy, easing the joint partner-income assessment, and disregarding savings for a fixed period---the last consistent with, though not testable on, FRS data that carry no household capital. The grid prices the first of these directly: moving assumed take-up among the newly entitled from 0.80 to 1.00 is worth about 2.6 points of displacement cushioning under the full schedule, and moving from 0.55 to 1.00 about 6.0. That is the size of the prize from making out-of-work support behave more like the tax schedule---it is not a way of closing a level gap, since on the corrected numbers there is barely one, but a way of removing the behavioural variance that only the extensive margin carries. Second, extending the duration or level of contribution-based new-style JSA, the instrument that reaches displaced workers regardless of take-up frictions and partner income---a UK analogue of earnings-related unemployment insurance, and the cleanest way to convert contingent protection into automatic protection. Third, wage insurance in the spirit of \citet{hyman2024}, which subsidises re-employment at lower wages: in the language of this paper it converts a displacement-margin realisation of the shock into a wage-cut-margin one, and Sections~\ref{sec:results-cushioning} and~\ref{sec:results-reallocation} show that margin is cushioned at least as well and, critically, without any dependence on claiming behaviour. Throughout, the revenue-recycling caveat of \citet{ignatenko2025} applies: this paper prices reforms in a first-round world with fiscal policy otherwise fixed, and financing choices can alter even the sign of aggregate employment effects.
