\begin{thebibliography}{99}

\bibitem[ABPI(2025)]{abpi2025}
ABPI (2025).
\newblock UK--US agreement on pharmaceutical tariffs and pricing.
\newblock Association of the British Pharmaceutical Industry, London, December 2025.

\bibitem[Acemoglu et~al.(2016)]{acemoglu2016}
Acemoglu, D., Akcigit, U. and Kerr, W. (2016).
\newblock Networks and the macroeconomy: An empirical exploration.
\newblock \emph{NBER Macroeconomics Annual}, 30(1), 273--335.

\bibitem[Acosta and Cox(2024)]{acostacox2024}
Acosta, M. and Cox, L. (2024).
\newblock The regressive nature of the US tariff code: Origins and implications.
\newblock Working paper, February 2024 (conditionally accepted, \emph{The Quarterly Journal of Economics}).

\bibitem[Ad\~{a}o et~al.(2023)]{adao2023}
Ad\~{a}o, R., Arkolakis, C. and Esposito, F. (2023).
\newblock General equilibrium effects in space: Theory and measurement.
\newblock NBER Working Paper No.~25544, National Bureau of Economic Research, Cambridge, MA.

\bibitem[Amiti et~al.(2019)]{amiti2019}
Amiti, M., Redding, S.~J. and Weinstein, D.~E. (2019).
\newblock The impact of the 2018 tariffs on prices and welfare.
\newblock \emph{Journal of Economic Perspectives}, 33(4), 187--210.

\bibitem[Arag\'{o}n et~al.(2018)]{aragon2018}
Arag\'{o}n, F.~M., Rud, J.~P. and Toews, G. (2018).
\newblock Resource shocks, employment, and gender: Evidence from the collapse of the UK coal industry.
\newblock \emph{Labour Economics}, 52, 54--67.

\bibitem[Atkin et~al.(2025)]{atkin2025}
Atkin, D., Bernadac, V., Donaldson, D., Garg, T. and Huneeus, F. (2025).
\newblock The incidence of distortions.
\newblock Working paper, December 2025 draft.

\bibitem[Auray et~al.(2020)]{auray2020}
Auray, S., Devereux, M.~B. and Eyquem, A. (2020).
\newblock Trade wars, currency wars.
\newblock NBER Working Paper No.~27460, National Bureau of Economic Research, Cambridge, MA.

\bibitem[Autor et~al.(2013)]{autor2013}
Autor, D.~H., Dorn, D. and Hanson, G.~H. (2013).
\newblock The China syndrome: Local labor market effects of import competition in the United States.
\newblock \emph{American Economic Review}, 103(6), 2121--2168.

\bibitem[Autor et~al.(2014)]{autor2014}
Autor, D.~H., Dorn, D., Hanson, G.~H. and Song, J. (2014).
\newblock Trade adjustment: Worker-level evidence.
\newblock \emph{The Quarterly Journal of Economics}, 129(4), 1799--1860.

\bibitem[Autor et~al.(2021)]{autor2021}
Autor, D.~H., Dorn, D. and Hanson, G.~H. (2021).
\newblock On the persistence of the China shock.
\newblock \emph{Brookings Papers on Economic Activity}, Fall 2021, 381--447.

\bibitem[Bank of England(2025)]{boe2025}
Bank of England (2025).
\newblock \emph{Monetary Policy Report}, May, August and November 2025 issues.
\newblock Bank of England, London.

\bibitem[Barrot and Sauvagnat(2016)]{barrotsauvagnat2016}
Barrot, J.-N. and Sauvagnat, J. (2016).
\newblock Input specificity and the propagation of idiosyncratic shocks in production networks.
\newblock \emph{The Quarterly Journal of Economics}, 131(3), 1543--1592.

\bibitem[Beatty and Fothergill(2017)]{beatty2017}
Beatty, C. and Fothergill, S. (2017).
\newblock The impact on welfare and public finances of job loss in industrial Britain.
\newblock \emph{Regional Studies, Regional Science}, 4(1), 161--180.

\bibitem[Beatty et~al.(2007)]{beatty2007}
Beatty, C., Fothergill, S. and Powell, R. (2007).
\newblock Twenty years on: Has the economy of the UK coalfields recovered?
\newblock \emph{Environment and Planning A}, 39(7), 1654--1675.

\bibitem[Beatty and Fothergill(2023)]{beatty2023}
Beatty, C. and Fothergill, S. (2023).
\newblock The persistence of hidden unemployment among incapacity claimants in large parts of Britain.
\newblock \emph{Local Economy}, doi:10.1177/02690942231184815.

\bibitem[Blanchard et~al.(2019)]{blanchard2019}
Blanchard, E.~J., Bown, C.~P. and Chor, D. (2019).
\newblock Did Trump's trade war impact the 2018 election?
\newblock NBER Working Paper No.~26434, National Bureau of Economic Research, Cambridge, MA.

\bibitem[Bloom et~al.(2019)]{bloom2019}
Bloom, N., Bunn, P., Chen, S., Mizen, P., Smietanka, P. and Thwaites, G. (2019).
\newblock The impact of Brexit on UK firms.
\newblock NBER Working Paper No.~26218, National Bureau of Economic Research, Cambridge, MA.

\bibitem[Borusyak and Jaravel(2021)]{borusyakjaravel2021}
Borusyak, K. and Jaravel, X. (2021).
\newblock The distributional effects of trade: Theory and evidence from the United States.
\newblock NBER Working Paper No.~28957, National Bureau of Economic Research, Cambridge, MA.

\bibitem[Bourguignon et~al.(2008)]{bourguignon2008}
Bourguignon, F., Bussolo, M. and Pereira~da Silva, L.~A. (eds.) (2008).
\newblock \emph{The Impact of Macroeconomic Policies on Poverty and Income Distribution: Macro-Micro Evaluation Techniques and Tools}.
\newblock Palgrave Macmillan and World Bank, Washington, DC.

\bibitem[Brewer and Tasseva(2021)]{brewertasseva2021}
Brewer, M. and Tasseva, I.~V. (2021).
\newblock Did the UK policy response to Covid-19 protect household incomes?
\newblock \emph{The Journal of Economic Inequality}, 19(3), 433--458.

\bibitem[Budget Lab(2025)]{budgetlab2025}
The Budget Lab (2025).
\newblock Where we stand: The fiscal, economic, and distributional effects of all U.S. tariffs enacted in 2025.
\newblock The Budget Lab at Yale, New Haven, CT.

\bibitem[Caliendo et~al.(2019)]{caliendo2019}
Caliendo, L., Dvorkin, M. and Parro, F. (2019).
\newblock Trade and labor market dynamics: General equilibrium analysis of the China trade shock.
\newblock \emph{Econometrica}, 87(3), 741--835.

\bibitem[Cavallo et~al.(2021)]{cavallo2021}
Cavallo, A., Gopinath, G., Neiman, B. and Tang, J. (2021).
\newblock Tariff pass-through at the border and at the store: Evidence from US trade policy.
\newblock \emph{American Economic Review: Insights}, 3(1), 19--34.

\bibitem[Cavallo et~al.(2025)]{cavallo2025}
Cavallo, A., Llamas, P. and Vazquez, F. (2025).
\newblock Tracking the short-run price impact of U.S. tariffs.
\newblock NBER Working Paper No.~34496, National Bureau of Economic Research, Cambridge, MA.

\bibitem[CEP(2025)]{cepdmp2025}
Centre for Economic Performance (2025).
\newblock UK firms and the 2025 US tariffs: Evidence from the Decision Maker Panel.
\newblock CEP/LSE and VoxEU analyses, London.

\bibitem[Centre for Cities(2025)]{centreforcities2025}
Centre for Cities (2025).
\newblock The uneven storm: How US tariffs hit UK cities differently.
\newblock Centre for Cities, London.

\bibitem[City-REDI(2025)]{cityredi2025}
City-REDI (2025).
\newblock The regional impact of US automotive tariffs on the UK economy.
\newblock City-REDI, University of Birmingham.

\bibitem[Corsetti et~al.(2025)]{corsettilloydostry2025}
Corsetti, G., Lloyd, S. and Ostry, D. (2025).
\newblock Trading blows: The exchange-rate response to tariffs and retaliations.
\newblock Staff Working Paper No.~1,139, Bank of England, London.

\bibitem[Dauth et~al.(2021)]{dauth2021}
Dauth, W., Findeisen, S. and Suedekum, J. (2021).
\newblock Adjusting to globalization in Germany.
\newblock \emph{Journal of Labor Economics}, 39(1), 263--302.

\bibitem[De~Lyon and Pessoa(2021)]{delyonpessoa2021}
De~Lyon, J. and Pessoa, J.~P. (2021).
\newblock Worker and firm responses to trade shocks: The UK--China case.
\newblock \emph{European Economic Review}, 133, 103678.

\bibitem[den Besten and K\"{a}nzig(2025)]{denbestenkanzig2025}
den Besten, T. and K\"{a}nzig, D.~R. (2025).
\newblock The macroeconomic effects of tariffs: Evidence from U.S. historical data.
\newblock NBER Working Paper No.~34852, National Bureau of Economic Research, Cambridge, MA.

\bibitem[Dhingra(2025)]{dhingra2025}
Dhingra, S. (2025).
\newblock Tariffed with the same brush.
\newblock Speech, Bank of England, October 2025.

\bibitem[Dhingra et~al.(2017)]{dhingra2017}
Dhingra, S., Ottaviano, G., Sampson, T. and Van~Reenen, J. (2017).
\newblock The costs and benefits of leaving the EU: Trade effects.
\newblock \emph{Economic Policy}, 32(92), 651--705.

\bibitem[Dix-Carneiro(2014)]{dixcarneiro2014}
Dix-Carneiro, R. (2014).
\newblock Trade liberalization and labor market dynamics.
\newblock \emph{Econometrica}, 82(3), 825--885.

\bibitem[Dix-Carneiro and Kovak(2017)]{dixcarneirokovak2017}
Dix-Carneiro, R. and Kovak, B.~K. (2017).
\newblock Trade liberalization and regional dynamics.
\newblock \emph{American Economic Review}, 107(10), 2908--2946.

\bibitem[Dolls et~al.(2012)]{dolls2012}
Dolls, M., Fuest, C. and Peichl, A. (2012).
\newblock Automatic stabilizers and economic crisis: US vs. Europe.
\newblock \emph{Journal of Public Economics}, 96(3--4), 279--294.

\bibitem[Dorn and Levell(2024)]{dorn2024}
Dorn, D. and Levell, P. (2024).
\newblock Labour market impacts of the China shock: Why the tide of globalisation did not lift all boats.
\newblock \emph{Labour Economics}, 91, 102629.

\bibitem[DWP(2024)]{dwp2024takeup}
Department for Work and Pensions (2024).
\newblock Income-related benefits: Estimates of take-up.
\newblock Official statistics series, DWP, London.

\bibitem[Fajgelbaum and Khandelwal(2016)]{fajgelbaumkhandelwal2016}
Fajgelbaum, P.~D. and Khandelwal, A.~K. (2016).
\newblock Measuring the unequal gains from trade.
\newblock \emph{The Quarterly Journal of Economics}, 131(3), 1113--1180.

\bibitem[Fajgelbaum and Khandelwal(2022)]{fajgelbaumkhandelwal2022}
Fajgelbaum, P.~D. and Khandelwal, A.~K. (2022).
\newblock The economic impacts of the US--China trade war.
\newblock \emph{Annual Review of Economics}, 14, 205--228.

\bibitem[Fajgelbaum and Khandelwal(2026)]{fajgelbaumkhandelwal2026}
Fajgelbaum, P.~D. and Khandelwal, A.~K. (2026).
\newblock Tariffs in 2025: Short-run impacts on the U.S. economy.
\newblock \emph{Brookings Papers on Economic Activity}, Spring 2026 conference draft.

\bibitem[Fajgelbaum et~al.(2020)]{fajgelbaum2020}
Fajgelbaum, P.~D., Goldberg, P.~K., Kennedy, P.~J. and Khandelwal, A.~K. (2020).
\newblock The return to protectionism.
\newblock \emph{The Quarterly Journal of Economics}, 135(1), 1--55.

\bibitem[Fetzer(2019)]{fetzer2019}
Fetzer, T. (2019).
\newblock Did austerity cause Brexit?
\newblock \emph{American Economic Review}, 109(11), 3849--3886.

\bibitem[Fetzer and Wang(2024)]{fetzerwang2024}
Fetzer, T. and Wang, S. (2024).
\newblock Measuring the regional economic cost of Brexit: Evidence up to 2019.
\newblock CAGE Working Paper No.~1280, University of Warwick.

\bibitem[Flaaen and Pierce(2019)]{flaaenpierce2019}
Flaaen, A. and Pierce, J.~R. (2019).
\newblock Disentangling the effects of the 2018--2019 tariffs on a globally connected U.S. manufacturing sector.
\newblock Finance and Economics Discussion Series 2019-086, Board of Governors of the Federal Reserve System, Washington, DC.

\bibitem[Galle et~al.(2023)]{galle2023}
Galle, S., Rodr\'{i}guez-Clare, A. and Yi, M. (2023).
\newblock Slicing the pie: Quantifying the aggregate and distributional effects of trade.
\newblock \emph{The Review of Economic Studies}, 90(1), 331--375.

\bibitem[Garin and Silv\'{e}rio(2024)]{garinsilverio2024}
Garin, A. and Silv\'{e}rio, F. (2024).
\newblock How responsive are wages to firm-specific changes in labour demand? Evidence from idiosyncratic export demand shocks.
\newblock \emph{The Review of Economic Studies}, 91(3), 1671--1710.

\bibitem[Gathmann et~al.(2020)]{gathmann2020}
Gathmann, C., Helm, I. and Sch\"{o}nberg, U. (2020).
\newblock Spillover effects of mass layoffs.
\newblock \emph{Journal of the European Economic Association}, 18(1), 427--468.

\bibitem[Hummels et~al.(2014)]{hummels2014}
Hummels, D., J\o{}rgensen, R., Munch, J. and Xiang, C. (2014).
\newblock The wage effects of offshoring: Evidence from Danish matched worker--firm data.
\newblock \emph{American Economic Review}, 104(6), 1597--1629.

\bibitem[Hyman et~al.(2024)]{hyman2024}
Hyman, B., Kovak, B.~K. and Leive, A. (2024).
\newblock Wage insurance for displaced workers.
\newblock NBER Working Paper No.~32464, National Bureau of Economic Research, Cambridge, MA.

\bibitem[IFS(2024)]{ifs2024}
Institute for Fiscal Studies (2024).
\newblock Health-related benefit claims post-pandemic: UK trends and global context.
\newblock IFS Report, Institute for Fiscal Studies, London, September 2024.

\bibitem[IMF(2025)]{imf2025}
International Monetary Fund (2025).
\newblock \emph{World Economic Outlook: Global Economy in Flux, Prospects Remain Dim}.
\newblock IMF, Washington, DC, October 2025.

\bibitem[Ignatenko et~al.(2025)]{ignatenko2025}
Ignatenko, A., Lashkaripour, A., Macedoni, L. and Simonovska, I. (2025).
\newblock Making America great again? The economic impacts of Liberation Day tariffs.
\newblock \emph{Journal of International Economics}, 157, 104138.

\bibitem[Irastorza-Fadrique et~al.(2025)]{irastorza2025}
Irastorza-Fadrique, A., Levell, P. and Parey, M. (2025).
\newblock Household responses to trade shocks.
\newblock \emph{Journal of International Economics}, forthcoming (IFS Working Paper 24/52).

\bibitem[Jeanne and Son(2024)]{jeanneson2024}
Jeanne, O. and Son, J. (2024).
\newblock To what extent are tariffs offset by exchange rates?
\newblock \emph{Journal of International Money and Finance}, 142.

\bibitem[Kalemli-\"{O}zcan et~al.(2026)]{kalemliozcan2026}
Kalemli-\"{O}zcan, \c{S}., Soylu, C. and Yildirim, M.~A. (2026).
\newblock Global trade, tariff uncertainty and the U.S. dollar.
\newblock NBER Working Paper No.~34728, National Bureau of Economic Research, Cambridge, MA.

\bibitem[Kim and Vogel(2021)]{kimvogel2021}
Kim, R. and Vogel, J. (2021).
\newblock Trade shocks and labor market adjustment.
\newblock \emph{American Economic Review: Insights}, 3(1), 115--130.

\bibitem[Michelena et~al.(2025)]{michelena2025}
Michelena, G., Ernst, C. and Bertin, P. (2025).
\newblock Tariffs and labor markets: The employment impact of the recent trade conflict. A multiregional input--output analysis.
\newblock International Labour Organization / arXiv:2512.11578, December 2025.

\bibitem[Moretti(2010)]{moretti2010}
Moretti, E. (2010).
\newblock Local multipliers.
\newblock \emph{American Economic Review: Papers \& Proceedings}, 100(2), 373--377.

\bibitem[Navicke et~al.(2013)]{navicke2013}
Navicke, J., Rastrigina, O. and Sutherland, H. (2013).
\newblock Nowcasting indicators of poverty risk in the European Union: A microsimulation approach.
\newblock EUROMOD Working Paper No.~EM11/13, ISER, University of Essex.

\bibitem[NIESR(2024)]{niesr2024}
NIESR (2024).
\newblock Implications of higher US tariffs for the UK economy.
\newblock National Institute of Economic and Social Research, London, December 2024.

\bibitem[OBR(2025)]{obr2025}
Office for Budget Responsibility (2025).
\newblock \emph{Economic and Fiscal Outlook}, March 2025 (tariff scenario box).
\newblock OBR, London.

\bibitem[Peichl(2016)]{peichl2016}
Peichl, A. (2016).
\newblock Linking microsimulation and CGE models.
\newblock \emph{International Journal of Microsimulation}, 9(1), 167--174.

\bibitem[Resolution Foundation(2025a)]{resolutionfoundation2025}
Resolution Foundation (2025a).
\newblock Trump tariff turmoil.
\newblock Resolution Foundation, London, April 2025.

\bibitem[Resolution Foundation(2025b)]{resolutionfoundation2025saving}
Resolution Foundation (2025b).
\newblock Saving penalties: Reforming the capital rules in Universal Credit.
\newblock Resolution Foundation, London, April 2025.

\bibitem[Roberts and Taylor(2022)]{robertstaylor2022}
Roberts, J. and Taylor, K. (2022).
\newblock New evidence on disability benefit claims in Britain: The role of health and the local labour market.
\newblock \emph{Economica}, 89(353), 131--160.

\bibitem[Rodr\'{i}guez-Clare et~al.(2025)]{rodriguezclare2025}
Rodr\'{i}guez-Clare, A., Ulate, M. and Vasquez, J.~P. (2025).
\newblock The 2025 trade war: Dynamic impacts across U.S. states and the global economy.
\newblock NBER Working Paper No.~33792, National Bureau of Economic Research, Cambridge, MA.

\bibitem[Rud et~al.(2022)]{rud2022}
Rud, J.~P., Simmons, M., Toews, G. and Arag\'{o}n, F. (2022).
\newblock Job displacement costs of phasing out coal.
\newblock IZA Discussion Paper No.~15581.

\bibitem[Sutherland and Figari(2013)]{sutherlandfigari2013}
Sutherland, H. and Figari, F. (2013).
\newblock EUROMOD: The European Union tax--benefit microsimulation model.
\newblock \emph{International Journal of Microsimulation}, 6(1), 4--26.

\bibitem[Tax Policy Center(2025)]{tpc2025}
Tax Policy Center (2025).
\newblock Description of the Tax Policy Center's tariff models.
\newblock Urban--Brookings Tax Policy Center, Washington, DC.

\bibitem[Traiberman(2019)]{traiberman2019}
Traiberman, S. (2019).
\newblock Occupations and import competition: Evidence from Denmark.
\newblock \emph{American Economic Review}, 109(12), 4260--4301.

\bibitem[Waugh(2019)]{waugh2019}
Waugh, M.~E. (2019).
\newblock The consumption response to trade shocks: Evidence from the US--China trade war.
\newblock NBER Working Paper No.~26353, National Bureau of Economic Research, Cambridge, MA.

\bibitem[WTO(2025)]{wto2025}
World Trade Organization (2025).
\newblock \emph{Global Trade Outlook and Statistics: Update October 2025}.
\newblock WTO, Geneva.

\end{thebibliography}
