\documentclass[11pt]{article}
\usepackage[margin=1.1in]{geometry}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{xcolor}
% Paper chrome uses the firm-microsim template blue (YGTemplate MyBlue);
% figures use the PolicyEngine palette separately.
\definecolor{paperblue}{rgb}{0,0,0.7}   % MyBlue, matching the sister papers
\definecolor{peteal}{HTML}{39C6C0}      % PolicyEngine teal accent
\usepackage{sectsty}
\allsectionsfont{\color{paperblue}}
\usepackage[hang,flushmargin]{footmisc}
\usepackage[colorlinks=true, citecolor=paperblue, linkcolor=paperblue, urlcolor=paperblue]{hyperref}
\hypersetup{
  pdftitle={Tax--Benefit Incidence under Alternative Labour-Market Stress Scenarios: A UK Tariff Application},
  pdfauthor={Vahid Ahmadi},
  pdfsubject={UK tax--benefit microsimulation under trade-related labour-income stress scenarios},
  pdfkeywords={tariffs, trade shocks, microsimulation, poverty, inequality, public finances}
}
\usepackage{natbib}
\bibliographystyle{apalike}

\title{\bfseries Tax--Benefit Incidence under Alternative Labour-Market Stress Scenarios\\[0.15cm] A UK Tariff Application\thanks{\textbf{Acknowledgements:} This is an open, reproducible research project. The author thanks PolicyEngine contributors for the underlying microsimulation infrastructure. All interpretations and remaining errors are the author's own.}\\[0.7cm]}
\author{Vahid Ahmadi\thanks{Research Associate at PolicyEngine. Email: \href{mailto:vahid@policyengine.org}{vahid@policyengine.org}.}}
\date{\small \ifcase\month\or January\or February\or March\or April\or May\or June\or July\or August\or September\or October\or November\or December\fi\ \the\year}

\input{generated_results}

\begin{document}
\maketitle

\begin{abstract}
\noindent This paper quantifies how much of an imposed trade-related labour-income stress the UK tax--benefit system absorbs, and how the answer changes when an earnings-equivalent loss is delivered through wage cuts, job displacement, inactivity or reallocation. Using Family Resources Survey households and PolicyEngine UK, it provides a statutory fiscal-incidence stress test calibrated to UK exposure to the 2025 US tariffs. Under the full schedule, the imposed direct earnings stress is \pounds0.886 billion annually; the system offsets \FullWageCushion\ per cent when the loss is delivered as wage cuts and \FullDisplacedCushion\ per cent on average under Bernoulli displacement. Equivalence across these margins holds in expectation, not in every assignment. The exercise is static, partial-equilibrium and first-round: it does not estimate tariff pass-through, production, productivity, labour demand, prices or total welfare. The tariff-to-wage-bill bridge and adjustment margins are imposed scenarios, not causal estimates. Results use \ProductionDraws\ assignments; assignment dispersion, numerical Monte Carlo error and parameter sensitivity are kept conceptually separate. The contribution is deliberately narrow: showing how adjustment margins reshape UK fiscal and distributional incidence conditional on a common expected labour-income loss.
\end{abstract}

\medskip
\noindent\textbf{Keywords:} tariffs, trade shocks, microsimulation, poverty, inequality, public finances

\smallskip
\noindent\textbf{JEL codes:} F13, F16, H23, I38, D31

\input{sections/summary}

\newpage
\input{sections/intro}
\input{sections/literature}
\input{sections/methodology}
\input{sections/results}
\input{sections/policy}
\input{sections/discussion}
\input{sections/declarations}

\input{sections/references}
\input{sections/appendix}

\end{document}
